%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Universität Hamburg}
\descript{| Summer Research Intern | \textcolor{Blue}{\href{https://github.com/shan18/taxi}{Github}}}
\location{June 2018 – August, 2018 | Hamburg, Germany}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Improved the existing method for taxonomy induction system called "TAXI" in the SemEval 2016 challenge on taxonomy extraction evaluation by introducing distributional semantics.
\item Developed a clustering mechanism, which clusters the nodes in the taxonomy, detaches the least similar clusters and adds them back at appropriate places using similarity scores.
\item Developed a method which would obtain the nodes which are not included in the taxonomy with respect to the gold standard for that particular domain and add them in appropriate places using similarity scores.
\item Used gensim (based on fasttext.cc) and poincare embeddings for similarity score calculations of family cluster and parent node respectively with the detached cluster/new node.
\item \custombold{Tools:} Python, NetworkX, Gensim, FastText, NLTK
\end{tightemize}
\sectionsep

\runsubsection{IIT Bombay}
\descript{| Summer Engineering Intern | \textcolor{Blue}{\href{https://github.com/shan18/SBHS-Vlabs}{Github}}}
\location{June 2017 – July 2017 | Mumbai, India}
\begin{tightemize}
\item Implementation of remote-triggered virtual labs using Django.
\item Worked on improving the efficiency and reliability of virtual lab systems.
\item Developed a mathematical model simulation for the Single Board Heating System.
\item Added an online quiz taking interface called yaksh.
\item Implemented a centralized database in order to prevent data inconsistency.
\item \custombold{Tools:} Python, Django, Scilab, Apache
\end{tightemize}
\sectionsep