%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Stock Bridge}
\descript{| Stock Market Simulator | \textcolor{Blue}{\href{https://github.com/morphosis-nitmz/Stock-Bridge}{Github}} | \textcolor{Blue}{\href{https://stock-bridge.herokuapp.com/}{Website}}}
\location{Apr 2018}
\begin{tightemize}
\item Built the entire user-company transaction system from scratch.
\item The fluctuations in stock prices completely automatic so that the fluctuations depend entirely on the number of transactions made during a fixed period of time.
\item Used signals, custom model managers, and custom querysets extensively.
\item Used the concept of coefficient of variation as a tiebreaker for the leaderboard.
\item Created a Bank model for the users to issue loan from and deduct interest from their loan amount accordingly.
\item \custombold{Tools:} Python, Django, Django REST Framework, Bootstrap v4, chart.js
\item \custombold{Services:} Amazon Web Services, Heroku, sendgrid
\end{tightemize}
\sectionsep

\runsubsection{Code Warrior}
\descript{| Online Judge Platform | \textcolor{Blue}{\href{https://github.com/morphosis-nitmz/Code-Warrior}{Github}} | \textcolor{Blue}{\href{https://code-warrior-morphosis.herokuapp.com/}{Website}}}
\location{Feb 2018 – Mar 2018}
\begin{tightemize}
\item Built the entire compilation, execution and submission evaluation module from scratch.
\item Made the platform to support following languages: C, C++, Python 2, Python 3
\item Used signals, custom model managers, and custom querysets extensively.
\item Used user submission execution time as a tiebreaker for the leaderboard.
\item Added the functionality to make the users see their previous submissions.
\item \custombold{Tools:} Python, Django, Bootstrap v4
\item \custombold{Services:} Amazon Web Services, sendgrid
\end{tightemize}
\sectionsep

\runsubsection{Kart}
\descript{| E-commerce Website | \textcolor{Blue}{\href{https://github.com/shan18/Kart}{Github}} | \textcolor{Blue}{\href{https://shan-kart.herokuapp.com/}{Website}}}
\location{Dec 2017 – Jan 2018}
\begin{tightemize}
\item Built the backend entirely on Django. Used jQuery in some places to make the website asynchronous.
\item Used signals, custom model managers and custom querysets extensively.
\item Built a search model which uses tags and helps the user to search over a wide range of products.
\item Built the functionality to sell digital items by storing them in AWS S3 Storage.
\item Render the order summary as a PDF and send it to the user after a successful transaction.
\item \custombold{Tools:} Python, Django, Bootstrap v4, jQuery, Ajax, jsrender, chart.js
\item \custombold{Services:} stripe, mailchimp, Amazon Web Services, heroku, sendgrid
\end{tightemize}
\sectionsep