\section{Projects \small{(Continued.)}}

\runsubsection{Stock Bridge}
\descript{| Stock Market Simulator | \textcolor{Blue}{\href{https://github.com/shan18/Stock-Bridge}{Github}} | \textcolor{Blue}{\href{https://stock-bridge.herokuapp.com/}{Website}}}
\location{Apr 2018} \vspace{0.1in}
\begin{tightemize}
\item Loaded the platform with real-world stock market features such as taking loans from bank, scheduling future transactions e.t.c.
\item Extensive usage of django signals, model managers and custom querysets.
\item \custombold{Tools:} Python, Django, Django REST Framework, chart.js, Bootstrap v4.
\item \custombold{Services:} Heroku, sendgrid.
\end{tightemize}
\sectionsep

\runsubsection{Code Warrior}
\descript{| Online Judge Platform | \textcolor{Blue}{\href{https://github.com/shan18/Code-Warrior}{Github}}}
\location{Feb 2018 – Mar 2018}
\begin{tightemize}
\item Designed the platform to support languages: C, C++, and Python.
\item Constructed a tiebreaker mechanism which uses user submission execution time for ranking users with the same score in the leaderboard.
\item \custombold{Tools:} Python, Django, Bootstrap v4.
\item \custombold{Services:} Amazon Web Services, PythonAnywhere, sendgrid.
\end{tightemize}
\sectionsep

\runsubsection{Kart}
\descript{| E-commerce Website | \textcolor{Blue}{\href{https://github.com/shan18/Kart}{Github}} | \textcolor{Blue}{\href{https://shan-kart.herokuapp.com/}{Website}}}
\location{Dec 2017 – Jan 2018}
\begin{tightemize}
\item Built the backend on entirely on Django. Utilized jQuery to make the website asynchronous.
\item Developed features like checkout with online payment, send order receipt via email, selling digital items e.t.c.
\item \custombold{Tools:} Python, Django, Bootstrap v4, jQuery, Ajax, chart.js, jsrender.
\item \custombold{Services:} stripe, mailchimp, Amazon Web Services, heroku, sendgrid.
\end{tightemize}
\sectionsep

\runsubsection{Autoranking Amazon Reviews}
\descript{| Machine Learning | Natural Language Processing | \textcolor{Blue}{\href{https://github.com/shan18/Autoranking-Amazon-Reviews}{Github}}}
\location{Oct 2017}
\begin{tightemize}
\item Created a model which can rank reviews on Amazon on the basis of their helpfulness.
\item Predictions were made based on various categories of features of the review text, and other metadata associated with the review, with the purpose of generating a rank for a given list of reviews.
\item \custombold{Tools:} Python, Numpy, Pandas, textblob, scikit-learn.
\end{tightemize}
\sectionsep

% \runsubsection{Morphosis}
% \descript{| Android | \textcolor{Blue}{\href{https://github.com/shan18/Morphosis}{Github}} | \textcolor{Blue}{\href{https://play.google.com/store/apps/details?id=com.nitmz.morphosis&hl=en}{Google Play Store}}}
% \location{Mar 2017 – Apr 2017 | Aizawl, Mizoram}
% \begin{tightemize}\item Created the android app for the annual technical fest of NIT Mizoram.
% \item The app contains the information of all the events which are to be conducted during the technical fest.
% \item Developed a game called Scooby Dooby Doo within the app.
% \item \custombold{Tools:} Java, Android Studio, Firebase.
% \end{tightemize}
% \sectionsep