%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Autoranking Amazon Reviews}
\descript{| Machine Learning | Natural Language Processing | \textcolor{Blue}{\href{https://github.com/shan18/Autoranking-Amazon-Reviews}{Github}}}
\location{Oct 2017 | Aizawl, Mizoram}
\begin{tightemize}
\item Ranking the reviews on Amazon according to their helpfulness score.
\item The problem was modeled as a regression problem. The performance was evaluated by using the the coefficient of determination and rank correlation.
\item Predictions were made based on various categories of features of the review text, and other metadata associated with the review, with the purpose of generating a rank for a given list of reviews.
\item \custombold{Tools:} Python, Numpy, Pandas, textblob, scikit-learn
\end{tightemize}
\sectionsep

\runsubsection{Morphosis}
\descript{| Android Application | \textcolor{Blue}{\href{https://github.com/shan18/Morphosis}{Github}} | \textcolor{Blue}{\href{https://play.google.com/store/apps/details?id=com.nitmz.morphosis&hl=en}{Google Play Store}}}
\location{Mar 2017 – Apr 2017 | Aizawl, Mizoram}
\begin{tightemize}\item Android App for the annual technical fest of NIT Mizoram
\item Contains all the information of various events to be conducted during the technical fest.
\item Live notification updates.
\item Contains a game called Scooby Dooby Doo, where participants have to answer various logical questions. The app gives live leader-board updates.
\item \custombold{Tools:} Java, Android Studio, Firebase
\end{tightemize}
\sectionsep